Viscous Transport in Eroding Porous Media

### 2019-08-22 docs/transport/erosion_transport.tex
edit the caption of figure in transport paper

>>>>

\begin{figure}[H]
\center
\includegraphics*[width =0.55\linewidth]{./figs/20b_dense_second_moment_ref}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous
dispersion in 20 nearly touching bodies with respect to initial porosity
(p=30.67\%) and another seven porosities during the eroding. The dashed line
correspondes to a porosity of 100\% and the dashed-dotted lines are lines
of best fit with slope 0.9194 (as p=95\%), 0.8666 (as p=85.17\%), 
0.8682 (as p=75.10\%), 0.9087 (as p=65.02\%), 
0.9054 (as p=55.08\%), 0.7234 (as p=45.03\%), 
0.6895 (as p=35.05\%), and 0.9225 (as p=30.67\%).}
\end{figure}
